Prediction of the 2020 Presidential Election

### 2020-11-03 outputs/paper/paper.Rmd

```{r, echo=FALSE}
 htst <- hoslem.test(final_model$y, fitted(final_model), g=10)
htst
```
Before the model can be used for any predictions, we must also check that our model fits our data well, and meets any assumptions made by the model. The Hosmer-Lemeshow goodness of fit test assesses whether or not the observed events match expected events in subgroups of the model. For this test, the p-value can be used to assess goodness of fit. A smaller p-value indicates strong evidence against a good fit. In the case of our model, we can see in table 4 that we have a very large p-value of 0.9, indicating no evidence of poor fit.

>>>>

```{r, echo=FALSE}
 htst <- hoslem.test(final_model$y, fitted(final_model), g=10)
```
Before the model can be used for any predictions, we must also check that our model fits our data well, and meets any assumptions made by the model. The Hosmer-Lemeshow goodness of fit test assesses whether or not the observed events match expected events in subgroups of the model. For this test, the p-value can be used to assess goodness of fit. A smaller p-value indicates strong evidence against a good fit. In the case of our model, we can see in table 4 that we have a very large p-value of 0.9, indicating no evidence of poor fit.
